A new type of generic, self-evolving and efficient automated deduction algorithm based on category theory

### 2023-05-20 zip/Math-7081.tex
wow accepted!

\def\typeofarticle{}
\def\currentvolume{}
\def\currentissue{}
\def\currentyear{}
\def\currentmonth{}
\def\ppages{}
\def\DOI{}
\def\Received{}
\def\Revised{}
\def\Accepted{}
\def\Published{}

@@

\begin{document}
	\title{A new type of generic, self-evolving and efficient automated deduction algorithm based on category theory}
	\author{%
		Zijian Wang\affil{1}
		Shao Xinhui\affil{*}
	}
	\shortauthors{the Authors}
	\address{%
		\addr{\affilnum{1}}{Northeast Yucai School, Zhenxing St. 9-5, Heping District, Shenyang, Liaoning, P.R.China. Email: felix\_wzj@yahoo.com}
		\corraddr{Department of Mathematics, College of Sciences, Northerneastern University, Shenyang, Liaoning, P.R.China. Email: shaoxinhui@mail.neu.edu.cn}
	}

>>>>

\def\typeofarticle{Research article}
\def\currentvolume{}
\def\currentissue{}
\def\currentyear{}
\def\currentmonth{}
\def\ppages{}
\def\DOI{}
\def\Received{}
\def\Revised{}
\def\Accepted{}
\def\Published{}

@@

\begin{document}
	\title{A new type of generic, self-evolving and efficient automated deduction algorithm based on category theory}
	\author{%
		Zijian Wang\affil{1}
		Shao Xinhui\affil{2,*}
	}
	\shortauthors{the Authors}
	\address{%
		\addr{\affilnum{1}}{Northeast Yucai School, Zhenxing St. 9-5, Heping District, Shenyang, Liaoning, P.R.China.}
		\addr{\affilnum{2}}{Department of Mathematics, College of Sciences, Northerneastern University, Shenyang, Liaoning, P.R.China. }
		\corraddr{Email: shaoxinhui@mail.neu.edu.cn}
	}
